Global well-being and mental health in the internet age

### 2023-05-10 ms.Rmd
Update authors

---
title: Global well-being and mental health in the internet age
shorttitle: Global well-being
leftheader: Global well-being
author: 
  - name: Matti Vuorre
    affiliation: 1
    address: Oxford Internet Institute, University of Oxford
    email: matti.vuorre@oii.ox.ac.uk
  - name: Andrew K. Przybylski
    affiliation: 1
    corresponding: yes
    address: Oxford Internet Institute, University of Oxford
    email: andy.przybylski@oii.ox.ac.uk
affiliation:
  - id: 1
    institution: Oxford Internet Institute, University of Oxford
authornote: |
  \noindent \textbf{This pre-print is not yet peer-reviewed.}
abstract: | 
  In the last two decades the rise of internet technologies have impacted nearly all domains of human life and inspired concern that their widespread adoption has impacted mental health and psychological well-being. However, research on the topic is contested and hampered by methodological shortcomings leaving the broader consequences of internet adoption unknown. We show that the past two decades have seen small and inconsistent changes in global well-being and mental health. The broadest available health and internet technology data does not support the idea that the adoption of internet and mobile broadband is consistently linked to negative psychological outcomes. However, associations between internet technology adoption and depression and self-harm were strongest (albeit still small) for individuals aged between 10 and 34. Further investigation of this topic requires transparent study of online behaviours where they occur, namely on online platforms. We call for increased collaborative efforts between independent scientists and the internet technology sector.

>>>>

---
title: Global well-being and mental health in the internet age
shorttitle: Global well-being
leftheader: Global well-being
author: 
  - name: Matti Vuorre
    affiliation: "1,2"
    address: Tilburg University
    email: m.j.vuorre@tilburguniversity.edu
  - name: Andrew K. Przybylski
    affiliation: "2"
    corresponding: yes
    email: andy.przybylski@oii.ox.ac.uk
affiliation:
  - id: 1
    institution: Tilburg School of Social and Behavioral Sciences, Tilburg University
  - id: 2
    institution: Oxford Internet Institute, University of Oxford
authornote: |
  \noindent \textbf{This pre-print is not yet peer-reviewed.}
abstract: | 
  In the last two decades the rise of internet technologies have impacted nearly all domains of human life and inspired concern that their widespread adoption has impacted mental health and psychological well-being. However, research on the topic is contested and hampered by methodological shortcomings leaving the broader consequences of internet adoption unknown. We show that the past two decades have seen small and inconsistent changes in global well-being and mental health. The broadest available health and internet technology data does not support the idea that the adoption of internet and mobile broadband is consistently linked to negative psychological outcomes. However, associations between internet technology adoption and depression and self-harm were strongest (albeit still small) for individuals aged between 10 and 34. Further investigation of this topic requires transparent study of online behaviours where they occur, namely on online platforms. We call for increased collaborative efforts between independent scientists and the internet technology sector.
